\chapter*{Acknowledgements}

\addcontentsline{toc}{chapter}{Acknowledgements}

\par This work was made possible by financial support from Science and Technology Facility Council (STFC) and the Royal Astronomical Society (RAS).
\par I would like to express sincere gratitude to my supervisor Dr. Diego Altamirano, referred to in this thesis as \textsf{D.A.}.  Without his experience, \textit{incredible} patience and willingness to push me to improve myself, this work would not have been possible.
\par I would like to thank Professor Tomaso Belloni, Professor Ranjeev Misra and Dr Andrea Sanna for hosting me at their respective institutes at various times in my studies.  I would also like to acknowledge the co-authors on papers I have produced during this PhD:
\begin{itemize}
\item Professor Tomaso Belloni, referred to in this thesis as \textsf{T.B.}, for many insightful discussions regarding IGR J17091-3624 and assistance with producing Figures \ref{fig:global_ob}, \ref{fig:ob_evo1} and \ref{fig:ob_evo2}.
\item Dr Andrea Sanna, referred to in this thesis as \textsf{A.S.}, for contributing pulsar pulse analysis to the results presented in Chapters \ref{ch:BPbig} and \ref{ch:BPletter}.
\item Arianna Albayati, referred to in this thesis as \textsf{A.A.}, for performing the first round of analysis on the bursts in the Bursting Pulsar, and conceiving of the four classes presented in Chapter \ref{ch:BPbig}.
\item Professor Kazutaka Yamaoka, referred to in this thesis as \textsf{K.Y.}, for assisting in the reduction of \textit{Suzaku} data for work presented in Chapters \ref{ch:IGR} and \ref{ch:BPbig}.
\item Dr. Margarita Pereyra and Dr. Nathalie Degenaar, referred to in this thesis as \textsf{M.P.} and \textsf{N.D.} respectively, for assisting in the reduction of \textit{Chandra} data for work presented in Chapters \ref{ch:IGR} and \ref{ch:BPbig}.
\item Dr. Chris Boone, referred to in this thesis as \textsf{C.B.}, for assisting in the reduction and analysis of \textit{INTEGRAL} presented in Chapter \ref{ch:IGR}.
\item Dr. Adam Hill, for assisting in the reduction of \textit{Fermi} data.
\item Toyah Overton, referred to in this thesis as \textsf{T.O.}, for performing hardness-intensity analysis of the bursts in the Bursting Pulsar presented in Chapter \ref{ch:BPbig}.
\item Professor Rudy Wijnands, Professor Christian Knigge and Dr. Mayukh Pahari  for useful discussions and comments.
\end{itemize}
\par I also thank other members of the faculty for their support, including Professor Poshak Gandhi, Professor Tony Bird, Dr. Matt Middleton and Simon Harris (for Knowing How To Make Computers Do Things).
\par On a more personal note, I would like to thank my family for their unwavering support during this at-times arduous task.  I would like to thank Jacob Blamey, Rory Brown, Simon Duncan, Mahesh Herath, David Williams, Ryan Wood \& Paul Wright for helping me to survive the Master's Degree that enabled me to get to this point.  I thank the new friends I have made during my time in the time in the department, including (but not limited to) Pip Grylls, Steven Browett, Bella Boulderstone, Dr. John Coxon, Michael Johnson (who is the worst), Lisa Kelsey, Pete Boorman, Dr. Mayukh Pahari \& Dr. Aarran Shaw.  All of you have helped me immensely, whether you realise it or not.
\par I also thank the staff of Titchfield Haven National Nature Reserve, Lymington and Keyhaven Marshes Local Nature Reserve, and Farlington Marshes Wildlife Reserve, for maintaining these beautiful places and giving me somewhere calm to visit at the end of stressful weeks.
\par Finally I thank my mother and father for their undying support throughout this entire process.  My father for believing in me, for his constant pushing for me to succeed, and for spending an entire day sat in a car in insect-infested Delaware to feed my birdwatching habit.  My mother for her care and patience, for years of driving to Southampton on a weekly basis to make sure everything was okay and for always being a 2 hour train ride away with a roast dinner and a chicken \& chorizo.